T-reX\@: Quantifying waste and material footprints in current and future \\ Life Cycle Assessment (LCA) databases

### 2024-11-30 00_JCR-submission-folder_SECOND SUBMISSION/cas-dc-template.tex
update

An example of the output from the application of T-reX has been included in the supplementary material in~\autoref{sec:supplementary}, subsection s. The manipulated \texttt{ecoinvent} databases (which are the main product of T-reX) can be recreated by following the instructions in the package documentation~\citep{mcdowall2023T-reXdocs}.

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=16cm]{figures/T-reX-wastefootprint-totalANDcarbon.pdf}
    \caption{T-reX calculated supply chain inventories for the five Li-ion batteries in the case study, showing their `footprints' for: (a) total solid waste, and (b) carbon dioxide waste (from carbon capture and storage (CCS) only). The footprints were modelled with prospective LCA databases from 2020 to 2100 under the SSP2 scenario using the baseline and PkBudg500 RCPs of the REMIND model.}\label{fig:waste_totalANDcarbon}
\end{figure}
%!!!!

@@

T-reX elucidates the complex relationships between material demand, waste generation, and environmental impacts. This instrument enables detailed exploration of `footprints' and life cycle inventories---modelled externalities of human activities---and examines their connections to supply chain risks and potential environmental damage. T-reX is a step towards a better understanding of these interconnections for the practical realisation of sustainability and the circular economy.

>>>>

An example of the output from the application of T-reX has been included in the supplementary material in~\autoref{sec:supplementary}, appendix 6. The manipulated \texttt{ecoinvent} databases (which are the main product of T-reX) can be recreated by following the instructions in the package documentation~\citep{mcdowall2023T-reXdocs}.

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=16cm]{figures/T-reX-wastefootprint-totalANDcarbon.pdf}
    \caption{T-reX calculated supply chain inventories for the five Li-ion batteries in the case study, showing their `footprints' for: (a) total solid waste, and (b) carbon dioxide waste (produced from carbon capture and storage (CCS) only). The footprints were modelled with prospective LCA databases from 2020 to 2100 under the SSP2 scenario using the baseline and PkBudg500 RCPs of the REMIND model.}\label{fig:waste_totalANDcarbon}
\end{figure}
%!!!!

@@

It is essential that we elucidate the complex relationships between material demand and waste generation and environmental and social harms. The software we present in this article enables detailed exploration of `footprints' and life cycle inventories---modelled externalities of human activities---and examines their potential connections threats such as supply chain risks and environmental damage. T-reX is a step towards a better understanding of these interconnections for the practical realisation of sustainability and the circular economy.

### 2024-11-30 latex_files-DRAFTING/discussion.tex
update

The utility of T-reX in studies of future supply chains is limited by the fact that the currently available prospective databases focus largely on changes in the energy, steel, cement, and transport sectors~\citep{sacchi2023premisedocs}. As demonstrated in the results of the case study---where there were often very few scenario-temporal changes in many waste and material footprint indicators---the utility of prospective LCA is restricted if there is inadequate adoption of future background inventories. In particular, the inclusion of scenarios with future waste processing technology could greatly improve our predictions of waste and material flows and offer valuable insight into their potential impacts~\citep{bisinella2024wastelca}. A strong focus on enhancing these prospective databases is, thus, of critical importance to the future of prospective LCA, and by extension, to the development of the `circular economy'.

>>>>

The utility of T-reX in studies of future supply chains is limited by the fact that the currently available prospective databases focus largely on changes in the energy, steel, cement, and transport sectors~\citep{sacchi2023premisedocs}. As demonstrated in the results of the case study---where there were often very few scenario-temporal changes in many waste and material footprint indicators---the utility of prospective LCA is restricted if there is inadequate adoption of future background inventories. In particular, the inclusion of scenarios with future waste processing technology could greatly improve our predictions of waste and material flows and offer valuable insight into their potential impacts~\citep{bisinella2024wastelca}. A strong focus on enhancing these prospective databases is, thus, of critical importance to the future of prospective LCA, and by extension, to the development of the circular economy.
